---
output:
  html_document:
    css: ./knitr.css
    fig_caption: yes
    highlight: default
    keep_md: no
    number_sections: no
    theme: journal
    toc: yes
---

part 1 - trial planning tools

```{r}
## null and alternative
p0 <- 0.1
pa <- 0.3


## misc functions

bin1samp_power <- function(p0, pa, n, r) {
  bin1pow_ <- function(n, p, r) {
    sum(dbinom(seq(r, n), n, p))
  }
  
  c(type1 = bin1pow_(n, p0, r), type2 = 1 - bin1pow_(n, pa, r))
}

twostg_power <- function(p0, pa, n1, n2, r1, r2) {
  nul <- desmon::twostg(n1, n2, p0, r1, r2)$prob
  alt <- desmon::twostg(n1, n2, pa, r1, r2)$prob
  
  c(Pr.stop1.H0 = nul[[2L]], Pr.stop1.H1 = alt[[2L]],
    type1 = 1 - nul[[1L]], type2 = alt[[1L]],
    E.tot.n.H0 = n1 + n2 * (1 - nul[[2L]]),
    E.tot.n.H1 = n1 + n2 * (1 - alt[[2L]]))
}

dlt_table <- function(prob, digits = 2L) {
  res <- sapply(prob, function(pr) {
    dbinom(0L, 3L, pr) + dbinom(0L, 3L, pr) * dbinom(1L, 3L, pr)
  })
  
  res <- rbind(
    'Pr(DLT)' = prob,
    'Pr(Escalation)' = res
  )
  
  fmt <- sprintf('%%.%sf', digits)
  res[] <- sprintf(fmt, res)
  
  res
}

f <- function(x) {
  cat('\n')
  sprintf('95%% CI: %0.2f - %0.2f, width: %0.2f', x[1L], x[2L], diff(x[1:2]))
}
```

## `desmon` package

```{r, eval=FALSE}
## to install:
install.packages('devtools')
devtools::install_github('raredd/desmon')
```

**`desmon`**

>Performs various calculations related to design of studies with either failure time or binary endpoints, and also functions to facilitate monitoring and analysis of such studies, including group sequential studies with failure time endpoints and two stage and randomized phase II studies.

Commonly-used functions:

- one-sample: `bin1samp`, `binci`, `onearm`
- two-stage: `simon`, `twostg`, `twocon`
- two proportion: `b2p`, `b2n`
- time-to-event: `surv1samp`, `seqopr`
- log-rank power: `powlgrnk`, `powlgrnk6`

## Designs

### 3+3

```{r, results='hold'}
## probability of DLT
prob <- c(5, 1:5 * 10) / 100

dlt_table(prob)

n <- 3 + 10
f(desmon::binci(n / 2, n))
```

### one-sample, one-stage

```{r, results='hold'}
des <- desmon::bin1samp(p0, pa)
des

n <- des[['n']]
f(desmon::binci(n / 2, n))
```

### simon optimal

```{r, results='hold'}
des <- desmon::simon(p0, pa)$designs
des

n <- as.list(des[1L, ])
f(desmon::twocon(n$n1, n$n2, n$r1, round((n$n1 + n$n2) / 2)))

## compare
f(desmon::binci((n$n1 + n$n2) / 2, n$n1 + n$n2))

n$n1 + n$n2 * (1 - n$Pstop1.H0)
```

### one-sample, two-stage

```{r, results='hold'}
twostg_power(p0, pa, 15, 20, 1, 6)

f(desmon::twocon(15, 15, 1, (15 + 15) / 2))

## compare
f(desmon::binci((15 + 20) / 2, 15 + 20))
```

### two-sample

```{r, results='hold'}
des <- ceiling(desmon::b2n(pa, p0, power = 0.9))
des

desmon::b2p(pa, p0, des[1L] / 2, des[1L] / 2)

f(desmon::binci(des[1L] / 4, des[1L] / 2))
f(desmon::binci(des[1L] / 2, des[1L]))
```

## Statistical considerations

### 3+3

```{r, results='asis'}
desmon2::mtd_text(prob, ndose = 3, expansion = 12)
```

### one-sample, one-stage

```{r, results='asis'}
desmon2::bin1samp_text(p0, pa, outcome = 'overall response rate (ORR)')
```

### simon optimal

```{r, results='asis'}
desmon2::simon_text(p0, pa, outcome = 'overall response rate (ORR)')
```

### one-sample, two-stage

```{r, results='asis'}
desmon2::twostg_text(p0, pa, 15, 20, 1, 6, outcome = 'overall response rate (ORR)')
```

### two-sample

```{r, results='asis'}
desmon2::b2p_text(pa, p0, power = 0.9, r = 0.75, arms = c('treatment', 'placebo'))
```

## todo

```{r, eval=FALSE}
## improve
b2p_text(...)

## add
surv1samp_text(...)
seqopr_text(...)
```

---

```{r, eval=TRUE, include=TRUE, comment=NA}
sessionInfo()
```
